Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-11-10 paper/main.tex
sheaf artist
cat section

\begin{equation}
  \label{eq:artist:presheaf}
  \begin{tikzcd}[column sep=small]
    {\Gamma(U_1, \dtotalc)}                                       & {}                                                    & {\Gamma(U_2, \dtotalc)} \arrow[ll, "\iota^*"', hook'] \\
                                                                  &                                                       &                                                       \\
    U_1 \arrow[uu, "\sheaf_{\dtotal}"] \arrow[rr, "\iota"', hook] & {} \arrow[uu, "\sheaf_{\dtotal}" description, dotted] & U_2 \arrow[uu, "\sheaf_\dtotal"']                    
    \end{tikzcd}
\end{equation}

@@

\begin{equation}
  \vartist: \sheaf_{\dtotal} \rightarrow \sheaf_{\vartist}
  \label{eq:artist:artist}
\end{equation}

@@

\begin{equation}
  \label{eq:artist:morphism-of-sheaf-data}
  \begin{tikzcd}
    & \mathcal{\dtotalc} & \\
{} \arrow[rr, "\dfuncc", Rightarrow, shift right, shorten=3em] & & {} \\
    & \mathcal{\dbasec}^{op} \arrow[uu, "\sheaf_{\dtotalc}", bend left] \arrow[uu, "\sheaf_{\dtotalc}"', bend right] &   
\end{tikzcd}
\end{equation}

@@

A set $\Gamma(U_i, \gtotal)$ contains functions to generate arbitrary graphics with a shared continuity and display space, while the artist $\vartist$ is constructed such that it generates a single type of graphic, as described in \autoref{sec:artist:construction}. Therefore, the range of the the artist functor, which we denote $Im_{\vartist}$, is a sheaf map $Im_{\vartist}$. Since the artist is a morphism of sheafs
\begin{equation}
  \vartist: \mathcal{\dtotal} \rightarrow Im_{\vartist}
\end{equation}
it is by definition a natural transformation\cite{SheafMathematics2021,bradleyWhatNaturalTransformation}. This means that all morphisms $\varphi$ on $\mathcal{\dtotal}$ are expected to commute \cite{spanier1989algebraic,fongInvitationAppliedCategory2019}. This is the basis of the equivariance condition illustrated in \autoref{eq:artist:equivariance}

\begin{equation}
  \label{eq:artist:equivariance}
  \begin{tikzcd}
    \mathcal{\dtotal} \arrow[r, "\vartist"] \arrow[d, "\varphi \in {Hom_{\mathcal{\dfiber}}(\dfiber, \dfiber)}"'] & Im_{\vartist} \arrow[d, "\vartist_{\varphi}"] \\
    \mathcal{\dtotal} \arrow[r, "\vartist"] & Im_{\vartist}                                                 
  \end{tikzcd}
\end{equation}
which states that transforms on the data side $\varphi \in Hom_{\mathcal{\dfiber}}(\dfiber, \dfiber)$ have an approximately equivalent transform in the data side $\vartist_{\varphi \in Hom_{\mathcal{\dfiber}}}$. This commutativity property states that visualization library components must be implemented such that changes in data induce equivalent changes in the output, which is how visualization libraries can produce visualizations that satisfy Kindlmann and Scheidegger's correspondence principal that data and visual structure must match.

>>>>

\begin{equation}
  \label{eq:artist:presheaf}
  \begin{tikzcd}[column sep=small]
    {\Gamma(U_1, \dtotalc)}                                       & {}                                                    & {\Gamma(U_2, \dtotalc)} \arrow[ll, "\iota^*"', hook'] \\
                                                                  &                                                       &                                                       \\
    U_1 \arrow[uu, "\sheafc_{\dtotal}"] \arrow[rr, "\iota"', hook] & {} \arrow[uu, "\sheafc_{\dtotal}" description, dotted] & U_2 \arrow[uu, "\sheafc_\dtotal"']                    
    \end{tikzcd}
\end{equation}

@@

\begin{equation}
  \vartistc: \sheafc_{\dtotalc} \rightarrow \sheafc_{\vartistc}
  \label{eq:artist:artist}
\end{equation}

@@

\begin{equation}
  \label{eq:artist:morphism-of-sheaf-data}
  \begin{tikzcd}
    & \mathcal{\dtotalc} & \\
{} \arrow[rr, "\dfuncc", Rightarrow, shift right, shorten=3em] & & {} \\
    & \mathcal{\dbasec}^{op} \arrow[uu, "\sheafc_{\dtotalc}", bend left] \arrow[uu, "\sheafc_{\dtotalc}"', bend right] &   
\end{tikzcd}
\end{equation}

@@

A set $\Gamma(U_i, \gtotal)$ contains functions to generate arbitrary graphics with a shared continuity and display space, while the artist $\vartist$ is constructed such that it generates a single type of graphic, as described in \autoref{sec:artist:construction}. Therefore, the range of the the artist functor, which we denote $Im_{\vartist}$, is a sheaf map $Im_{\vartist}$.

Since the artist is a morphism of sheafs it is by definition a natural transformation\cite{SheafMathematics2021,bradleyWhatNaturalTransformation}. This means that all morphisms $\varphi$ on $\mathcal{\dtotal}$ are expected to commute \cite{spanier1989algebraic,fongInvitationAppliedCategory2019}. This is the basis of the equivariance condition illustrated in \autoref{eq:artist:equivariance}

\begin{equation}
  \label{eq:artist:equivariance}
  \begin{tikzcd}
    \sheafc_{\dtotalc} \arrow[r, "\vartistc"] \arrow[d, "\dfuncc_{\dtotalc}"'] & \sheafc_{\vartistc} \arrow[d, "\dfuncc_{\vartistc}"] \\
    \sheafc_{\dtotalc} \arrow[r, "\vartistc"] & \sheafc_{\vartistc}                                              
  \end{tikzcd}
\end{equation}
which states that transforms on the data side $\varphi \in Hom_{\mathcal{\dfiber}}(\dfiber, \dfiber)$ have an approximately equivalent transform in the data side $\vartist_{\varphi \in Hom_{\mathcal{\dfiber}}}$. This commutativity property states that visualization library components must be implemented such that changes in data induce equivalent changes in the output, which is how visualization libraries can produce visualizations that satisfy Kindlmann and Scheidegger's correspondence principal that data and visual structure must match.
